Current Affairs: Utilizing Oxford Nanopore Sequencing Data to Detect Non-Canonical DNA Structures

### 2024-01-27 jan30meeting_pres1/may30ccgmeeting.tex
updates

	\begin{frame}{Predicting Non-B Structures From Nanopore Sequencing}
		A recently published reference set of genome-wide cSLs common to many cancer types was utilized
		\begin{center}
				\includegraphics[width=6cm,height=6cm]{corenet.png}
		\end{center}
	\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}

	%EXPLAIN THE PROCESS OF ISLE HERE
	\begin{frame}{Building Pan-Cancer Synthetic Lethality Networks}
		\centering
		\includegraphics[width=13cm, height=7cm]{isle.png}
		%\movie[width=10cm,height=7cm,showcontrols=true]{\includegraphics[width=10cm, height=7cm]{pompe_thumbnail.png}}{pompe_trimmed.mp4}
		\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}

	%%% EXPLAIN NSSE SURVEY A BIT
	%%% WHEN YOU TALK MENTION THAT THEY DID THIS SURVEY AFTER PLAYING THE GAME IN CLASS
	\begin{frame}{There is Variability in Synthetic Lethal Interactions Depending on Cancer Type}

@@

	\begin{frame}{Sex Differences Add an Additional Layer of Complexity}
		Human sex differences are mainly caused by;
		\begin{enumerate}
			\item Gonadal hormone secretions
			\item Genes located on the sex chromosomes (X and Y) \newline
		\end{enumerate}
	This leads to differences in the frequency of certain cancer types and the efficacy of treatments in males and females
	\end{frame}

	\begin{frame}{Sex Differences Add an Additional Layer of Complexity}
		\centering
		\includegraphics[width=6cm,height=7cm]{sex.png}
		\footnotetext[6]{\tiny\cite{oliva2020impact}}
	\end{frame}

	\begin{frame}{The Objective}
		\begin{center}
		%\includegraphics[width=11cm, height=6cm]{types_of_courses_taken.jpg}
		Can we build sex-specific synthetic lethality networks for various cancer types? \newline

		More specifically, we are trying to elucidate the differences in synthetic lethal interactions between males and females using a network based approach.
		\end{center}
	\end{frame}

>>>>

	\begin{frame}{Predicting Non-B Structures From Nanopore Sequencing}
		A recently published paper utilized translocation times from ONT sequencing to predict non-B DNA structures (citation)
		\begin{itemize}
			\item Developed the first computational pipeline and a novel unsupervised deep statistical model for predicting non-B DNA structures \newline
		\end{itemize}

		Benefits  of unsupervised approach;
		\begin{enumerate}
			\item non-B database labels are noisy (just because motif is present does not mean structure is)
			\item Even if high quality labeling for non-B DNA were available, substantially more B-DNA samples are available
			\item Unknown non-B structures or non-B DNA without sequence motifs cannot be modelled by a supervised approach
		\end{enumerate}
	\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}

	%EXPLAIN THE PROCESS OF ISLE HERE
	\begin{frame}{GoFAE-DND: Deep Statistical modelling of non-B DNA}
		Anomaly Detection Problem: Identifying patterns within data that deviate significantly from the norm or expected behaviour of the majority of the data
		\begin{center}
		\includegraphics[width=12cm, height=5cm]{gofae.jpeg}
		\end{center}
		%\movie[width=10cm,height=7cm,showcontrols=true]{\includegraphics[width=10cm, height=7cm]{pompe_thumbnail.png}}{pompe_trimmed.mp4}
		\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}

	%%% EXPLAIN NSSE SURVEY A BIT
	%%% WHEN YOU TALK MENTION THAT THEY DID THIS SURVEY AFTER PLAYING THE GAME IN CLASS
	\begin{frame}{Results of the Model}

@@

	\begin{frame}{The Objective}
		Human sex differences are mainly caused by;
		\begin{enumerate}
			\item Gonadal hormone secretions
			\item Genes located on the sex chromosomes (X and Y) \newline
		\end{enumerate}
	This leads to differences in the frequency of certain cancer types and the efficacy of treatments in males and females
	\end{frame}

	\begin{frame}{Preprocessing Workflow}
		\centering
		\includegraphics[width=6cm,height=7cm]{sex.png}
		\footnotetext[6]{\tiny\cite{oliva2020impact}}
	\end{frame}
